Flesh Simulation in the Field of Animation

### 2020-03-07 LaTeX-Master-Vorlage/chapter/paper.tex
paper, depressed cube

\subsubsection{3D Volume Term}
The volume term of $\Psi_{Neo}$, meaning
\[
\Psi_{Neo, volume} = -\mu \log J+\frac{\lambda}{2}(\log J)^{2}
\]
results in some numerical problems since the logarithmic function is not defined for $J<0$ and grows unbounded for $J \rightarrow 0$. In conclusion $\Psi_{Neo, volume}$ is not singularity free. 
The same applies for the 3D volume term of $\Psi_{A}$, namely
\[
\Psi_{A, volume} = -\mu \log J+\frac{\lambda}{2}(J-1)^{2}.
\]
The term of $\Psi_{A}$ and $\Psi_{B}$ which is of the form
\[
\Psi_{M} = \frac{\lambda}{2}(J-1)^{2}
\]
does not have these noted difficulties. It is bounded, well defined and invertible. After these observations we combine the robust length with the robust volume term and receive $\Psi_D$ that is defined as
\[
\Psi_{D} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-1)^{2}
\]
and is singularity free and well defined under inversion. Unfortunately $\Psi_D$ does not satisfy the requirement of being rest stable which will be discussed in the next section.

\todoredefined[inline]{
TODO: Bonet and Wood 2008 or 1997? Table looks ugly, improve and add resources. Improve English sentences. Overall okay concerning the content?
}

\subsection{Rest Stabilization}
Although $\Psi_{D}$ meets almost all stated requirements it is not rest stable. This can be shown with the Piola-Kirchhoff (PK1) stress tensor for $\Psi_D$ depending on the identity matrix $\mathbf{I}$:
\begin{align*}
P_{D}(\mathbf{I}) &= \frac{\partial \Psi_{D}}{\partial \mathbf{F}} (\mathbf{I}) = \frac{\partial \Psi_{D}}{\partial \mathbf{F}} \left[ \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-1)^{2} \right] \\
&= \frac{\partial \Psi_{D}}{\partial \mathbf{F}}  \frac{\mu}{2}\left(\operatorname{tr}(\mathbf{I}^\intercal \mathbf{I})-3\right) +\frac{\partial \Psi_{D}}{\partial \mathbf{F}} \frac{\lambda}{2}(\operatorname{tr}(\mathbf{I})-1)^{2} \\
&= \mu I + \lambda (\operatorname{det}(\mathbf{I})-1)  \frac{\partial}{\partial \mathbf{F}} \operatorname{det}(\mathbf{I}) = \mu \mathbf{I} \neq 0
\end{align*}

If the energy had rest stability $P_{D}(\mathbf{I})$ would resolve to zero. Unfortunately this is not the case here. In order to solve that problem the authors modified $(J-1)^{2}$ to $(J-\alpha)^{2}$. Using this modification the energy shifts to
\[
\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-\alpha)^{2}.
\]

Taking $\Psi_E$ in the PK1 equation from before we get
\begin{align*}
P_{E}(\mathbf{F}) &= \frac{\partial \Psi_{E}}{\partial \mathbf{F}} \left[ \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-\alpha)^{2} \right] \\
&= \mu \mathbf{F} + \lambda (\operatorname{det}(\mathbf{F})-\alpha)  \frac{\partial}{\partial \mathbf{F}} \operatorname{det}(\mathbf{F}).
\end{align*}
Solving for an alpha that satisfies $P_{E}(\mathbf{I})=0$ gives us $\alpha=1+\frac{\mu}{\lambda}$. Now $\Psi_{E}$ has to be changed accordingly:
\begin{align*}
\Psi_{E} &= \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-1-\frac{\mu}{\lambda})^{2} \\
&= \frac{\mu}{2}\left(I_{C}-3\right) - \mu\left(J-1\right) + \frac{\lambda}{2}(J-1)^{2} + \left(\frac{\mu}{\lambda}\right)^{2}.
\end{align*}
Since constant disappear under differentiation this expression is functionally equivalent to 
\[
\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) - \mu\left(J-1\right) + \frac{\lambda}{2}(J-1)^{2}.
\]
Now one can notice that $\Psi_{E}$ looks very similar to $\Psi_{Neo}$. The difference is that $log(J)$ is replaced with $(J-1)$ in $\Psi_{E}$. Remember that $(J-1)$ is the first term in the taylor approximation of $\operatorname{log}(J)$ at $J=1$:
\begin{align*}
\sum_{n=0}^{\infty} &= \frac{f^{(n)}(1)}{n!} (J-1)^{n} \\
&= \boldsymbol{(J-1)} - \frac{1}{2} (J-1)^{2} + \frac{1}{3} (J-1)^{3} -\frac{1}{4} (J-1)^{4} + ...
\end{align*}

@@

\subsection{Meta-Stability under Degeneracy}
The final energy is
\begin{equation}\label{eq:stable_energy}
\Psi_{new} = \frac{\mu}{2}\left(I_{C}-3\right) + \frac{\lambda}{2}(J-\alpha)^{2} - \frac{\mu}{2} \operatorname{log}\left(I_{C}+1\right).
\end{equation}
With that adjustment the rest stability term shifts to $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$.

@@

\section{Energy Analysis}
The goal of this chapter is to show that a complete eigenanalysis can be performed on equation \ref{eq:stable_energy}.

\subsection{First Piola-Kirchhoff Stress (PK1)}
In order to analyse the energy PK1 can be used for equation \ref{eq:stable_energy}:
\begin{align*}
P(\mathbf{F}) &= \frac{\partial \Psi_{D}}{\partial \mathbf{F}} \left[ \frac{\mu}{2}\left(I_{C}-3\right) + \frac{\lambda}{2}(J-\alpha)^{2} - \frac{\mu}{2}\left(I_{C}+1\right) \right] \\
&= \mu \mathbf{F} + \lambda (\operatorname{det}(\mathbf{F})-\alpha)  \frac{\partial}{\partial \mathbf{F}} \operatorname{det}(\mathbf{F}) - \frac{\partial}{\partial \mathbf{F}} \left[\operatorname{log}\left(\operatorname{tr}(\mathbf{F}^\intercal \mathbf{F})+1\right)\right] \\
&= \mu \mathbf{F} + \lambda (\operatorname{det}(\mathbf{F})-\alpha)  \frac{\partial}{\partial \mathbf{F}} \operatorname{det}(\mathbf{F}) - \mu \mathbf{F} \frac{1}{\operatorname{tr}(\mathbf{F}^\intercal \mathbf{F}) + 1} \\
&= \mu \left( 1 - \frac{1}{\operatorname{tr}(\mathbf{F}^\intercal \mathbf{F}) + 1}\right) \mathbf{F} + \lambda(J-\alpha)\frac{\partial J}{\partial \mathbf{F}}
\end{align*}

with $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$. For future use it can be more practical to write $\frac{\partial J}{\partial \mathbf{F}}$ as a result of cross products:
\begin{equation}\label{eq:cross_product}
\frac{\partial J}{\partial \mathbf{F}} = \left[ \,f_1 \times f_2\, \bigg| \,f_2 \times f_0\, \bigg| \,f_0 \times f_1\, \right].
\end{equation}

@@

\subsection{The Energy Hessian Terms}
Using the scalar notation for $\mathbf{F}$ the hessian of the energy can be written in a fourth-order matrix-of-matrices:
\[
\frac{\partial^2 \psi}{\partial \mathbf{F}^2} = \frac{\partial P(\mathbf{F})}{\partial \mathbf{F}} = 
\left[\begin{array}{ccc}{\left[\frac{\partial P(\mathbf{F})}{\partial f_0}\right]} & {\left[\frac{\partial P(\mathbf{F})}{\partial f_3}\right]} & {\left[\frac{\partial P(\mathbf{F})}{\partial f_6}\right]} \\ {\left[\frac{\partial P(\mathbf{F})}{\partial f_1}\right]} & {\left[\frac{\partial P(\mathbf{F})}{\partial f_4}\right]} & {\left[\frac{\partial P(\mathbf{F})}{\partial f_7}\right]} \\ {\left[\frac{\partial P(\mathbf{F})}{\partial f_2}\right]} & {\left[\frac{\partial P(\mathbf{F})}{\partial f_5}\right]} & {\left[\frac{\partial P(\mathbf{F})}{\partial f_8}\right]} \end{array}\right]
\]

in which each entry is defined as
\[
\frac{\partial P(\mathbf{F})}{\partial f_i} = \frac{\partial}{\partial f_i} \left[ \mu \left( 1 - \frac{1}{\operatorname{tr}(\mathbf{F}^\intercal \mathbf{F}) + 1}\right) \mathbf{F} + \lambda(J-\alpha)\frac{\partial J}{\partial \mathbf{F}} \right]
\]
\[
\stackrel{\text{prod.rule}}{=} \underbrace{\frac{\partial \mathbf{F}}{\partial f_i} \mu \left( 1 - \frac{1}{\operatorname{tr}(\mathbf{F}^\intercal \mathbf{F}) + 1}\right)}_{\mathrm{T}_{i}}  + \underbrace{\mathbf{F} \mu \frac{2}{\left(\operatorname{tr}(\mathbf{F^\intercal}\mathbf{F}) + 1\right)^2} f_i}_{_{\mathrm{M}_{i}}}
\]
\[
r+ \underbrace{\lambda \frac{\partial J}{\partial f_i} \frac{\partial J}{\partial \mathbf{F}}}_{_{\mathrm{G}_{i}}}+ \underbrace{\lambda (J- \alpha) \frac{\partial^2 J}{\partial \mathbf{F}\partial f_i}}_{_{\mathrm{H}_{i}}} \in \mathbb{R}^{3}.
\]
Each term in the final equation $\mathrm{T}_i$, $\mathrm{M}_i$, $\mathrm{G}_i$, $\mathrm{H}_i$ respectively the Tikohonov, Mu, volume Gradient and volume Hessian term will be examined separately in the following sections.

\subsection{The Tikhonov, Mu, and Gradient Terms}
\subsubsection{Tikhonov}
The Tikhonov term can be viewed as a fourth-order matrix-of-matrices
\[
\mathbb{T} = \frac{\partial \mathbf{F}}{\partial f_i} = \left[\begin{array}{ccc}{\begin{bmatrix} 1 & 0 & 0 \\ 0 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 1 & 0 \\ 0 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 1 \\ 0 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} \\ {\begin{bmatrix} 0 & 0 & 0 \\ 1 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 1 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 1 \\ 0 & 0 & 0 \end{bmatrix}} \\ {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 0 \\ 1 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 0 \\ 0 & 1 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 0 \\ 0 & 0 & 1 \end{bmatrix}} \end{array}\right].
\]
If we vectorize $\mathbb{T}$ we get the identity matrix $\mathbf{I} \in \mathbb{R}^{9x9}$ which is full rank, positive definite and independent of the values in F. It serves as a regularizer for the rest of the energy
\[
\operatorname{vec}(\mathbb{T}) =  \mathbf{\check{T}} = \mathbf{I} = \in \mathbb{R}^{9x9}.
\]

\subsubsection{Mu}
The Mu term has the same structure with different entries
\[
\mathbb{M} = \mathbf{F} f_i = \left[\begin{array}{ccc}{\begin{bmatrix} f_0^2 & f_0f_3 & f_0f_6 \\ f_0f_1 & f_0f_4 & f_0f_7 \\ f_0f_2 & f_0f_5 & f_0f_8 \end{bmatrix}} & {\begin{bmatrix} f_3f_0 & f_3^2 & f_3f_6 \\ f_3f_1 & f_3f_4 & f_3f_7 \\ f_3f_2 & f_3f_5 & f_3f_8 \end{bmatrix}} & {\begin{bmatrix} f_6f_0 & f_6f_3 & f_6f_6 \\ f_6f_1 & f_6f_4 & f_6f_7 \\ f_6f_2 & f_6f_5 & f_6f_8 \end{bmatrix}} \\ {\begin{bmatrix} f_1f_0 & f_1f_3 & f_1f_6 \\ f_1^2 & f_1f_4 & f_1f_7 \\ f_1f_2 & f_1f_5 & f_1f_8 \end{bmatrix}} & {\begin{bmatrix} f_4f_0 & f_4f_3 & f_4f_6 \\ f_4f_1 & f_4^2 & f_4f_7 \\ f_4f_2 & f_4f_5 & f_4f_8 \end{bmatrix}} & {\begin{bmatrix} f_7f_0 & f_7f_3 & f_7f_6 \\ f_7f_1 & f_7f_4 & f_7^2 \\ f_7f_2 & f_7f_5 & f_7f_8 \end{bmatrix}} \\ {\begin{bmatrix} f_2f_0 & f_2f_3 & f_2f_6 \\ f_2f_1 & f_2f_4 & f_2f_7 \\ f_2^2 & f_2f_5 & f_2f_8 \end{bmatrix}} & {\begin{bmatrix} f_5f_0 & f_5f_3 & f_5f_6 \\ f_5f_1 & f_5f_4 & f_5f_7 \\ f_5f_2 & f_5^2 & f_5f_8 \end{bmatrix}} & {\begin{bmatrix} f_8f_0 & f_8f_3 & f_8f_6 \\ f_8f_1 & f_8f_4 & f_8f_7 \\ f_8f_2 & f_8f_5 & f_8^2 \end{bmatrix}} \end{array}\right].
\]
When vectorizing $\mathbb{M}$ the resulting matrix has the squared values of $f_i$ placed on the diagonal
\[
\operatorname{vec}(\mathbb{M})= \mathbf{\check{M}} = \begin{bmatrix} f_0^2 & f_1f_0 & f_2f_0 & f_3f_0 & f_4f_0 & f_5f_0 & f_6f_0 & f_7f_0 & f_8f_0 \\ f_0f_1 & f_1^2 & f_2f_1 & f_3f_1 & f_4f_1 & f_5f_1 & f_6f_1 & f_7f_1 & f_8f_1 \\ f_0f_2 & f_1f_2 & f_2^2 & f_3f_2 & f_4f_2 & f_5f_2 & f_6f_2 & f_7f_2 & f_8f_2 \\ f_0f_3 & f_1f_3 & f_2f_3 & f_3^2 & f_4f_3 & f_5f_3 & f_6f_3 & f_7f_3 & f_8f_3 \\ f_0f_4 & f_1f_4 & f_2f_4 & f_3f_4 & f_4^2 & f_5f_4 & f_6f_4 & f_7f_4 & f_8f_4 \\ f_0f_5 & f_1f_5 & f_2f_5 & f_3f_5 & f_4f_5 & f_5^2 & f_6f_5 & f_7f_5 & f_8f_5 \\ f_0f_6 & f_1f_6 & f_2f_6 & f_3f_6 & f_4f_6 & f_5f_6 & f_6^2 & f_7f_6 & f_8f_6 \\ f_0f_7 & f_1f_7 & f_2f_7 & f_3f_7 & f_4f_7 & f_5f_7 & f_6f_7 & f_7^2 & f_8f_7 \\ f_0f_8 & f_1f_8 & f_2f_8 & f_3f_8 & f_4f_8 & f_5f_8 & f_6f_8 & f_7f_8 & f_8^2 \end{bmatrix}.
\]
This structure makes it possible to write $\mathbf{\check{M}}$ as an outer product of $\operatorname{vec}(\mathbf{F})$
\[
\mathbf{\check{M}}= \operatorname{vec}(\mathbf{F})\operatorname{vec}(\mathbf{F})^\intercal = \mathbf{\check{f}} \mathbf{\check{f}}^\intercal.
\]
This matrix has rank one and has a single non-zero eigenvalue. In order to examine the eigenvalues one can calculate
\[
\| \mathbf{\check{f}} \|^{2}_{2} = \sum_{n=0}^8 | f_n |^2 = \| \mathbf{F} \|^{2}_{F} = \sum_{n=0}^3 \sigma^2_i = \left( \sigma_0^2 + \sigma_1^2 + \sigma_2^2 \right)
\]
in which $\|\cdot\|_F$ stands for the Frobenius norm and $\sigma_i$ for the singular values from $\mathbf{\Sigma}$ in the SVD of $\mathbf{F}$ stated in eq. \ref{eq:svd_simga}. The eigenvector is $\mathbf{\check{f}} / \| \mathbf{\check{f}} \|$. The eigenvalue is always non-negative and large if $\mathbf{F}$ contains a large strech.

>>>>

\subsubsection{3D Volume Term}
The volume term of $\Psi_{Neo}$, meaning
\[
\Psi_{Neo, volume} = -\mu \log J+\frac{\lambda}{2}(\log J)^{2}
\]
results in some numerical problems since the logarithmic function is not defined for $J<0$ and grows unbounded for $J \rightarrow 0$. In conclusion $\Psi_{Neo, volume}$ is not singularity free. 
The same applies for the 3D volume term of $\Psi_{A}$, namely
\[
\Psi_{A, volume} = -\mu \log J+\frac{\lambda}{2}(J-1)^{2}.
\]
The term of $\Psi_{A}$ and $\Psi_{B}$ which is of the form
\[
\Psi_{M} = \frac{\lambda}{2}(J-1)^{2}
\]
does not have these problems. It is bounded, well defined and invertible. After these observations we combine the robust length with the robust volume term and receive $\Psi_D$ that is defined as
\[
\Psi_{D} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-1)^{2}
\]
and is singularity free and well defined under inversion. Unfortunately, $\Psi_D$ does not satisfy the requirement of being rest stable which will be discussed in the next section.

\todoredefined[inline]{
TODO: Bonet and Wood 2008 or 1997?
}

\subsection{Rest Stabilization}
Although $\Psi_{D}$ meets almost all stated requirements, it is not rest stable. This can be shown with the Piola-Kirchhoff (PK1) stress tensor for $\Psi_D$ derived by the deformation gradient \textbf{F}:
\begin{align*}
P_{D}(\mathbf{I}) &= \frac{\partial \Psi_{D}}{\partial \mathbf{F}} (\mathbf{I}) = \frac{\partial \Psi_{D}}{\partial \mathbf{F}} \left[ \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-1)^{2} \right] \\
&= \frac{\partial \Psi_{D}}{\partial \mathbf{F}}  \frac{\mu}{2}\left(\operatorname{tr}(\mathbf{I}^\intercal \mathbf{I})-3\right) +\frac{\partial \Psi_{D}}{\partial \mathbf{F}} \frac{\lambda}{2}(\operatorname{tr}(\mathbf{I})-1)^{2} \\
&= \mu I + \lambda (\operatorname{det}(\mathbf{I})-1)  \frac{\partial}{\partial \mathbf{F}} \operatorname{det}(\mathbf{I}) = \mu \mathbf{I} \neq 0
\end{align*}

If the energy had rest stability, $P_{D}(\mathbf{I})$ would resolve to zero. Unfortunately, this is not the case here. In order to solve that problem, the authors modified $(J-1)^{2}$ to $(J-\alpha)^{2}$. Using this modification the energy can written as
\[
\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-\alpha)^{2}.
\]

Inserting $\Psi_E$ into the PK1 equation from before, we get
\begin{align*}
P_{E}(\mathbf{F}) &= \frac{\partial \Psi_{E}}{\partial \mathbf{F}} \left[ \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-\alpha)^{2} \right] \\
&= \mu \mathbf{F} + \lambda (\operatorname{det}(\mathbf{F})-\alpha)  \frac{\partial}{\partial \mathbf{F}} \operatorname{det}(\mathbf{F}).
\end{align*}
Solving for an alpha that satisfies $P_{E}(\mathbf{I})=0$ gives us $\alpha=1+\frac{\mu}{\lambda}$. Now $\Psi_{E}$ has to be changed accordingly:
\begin{align*}
\Psi_{E} &= \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-1-\frac{\mu}{\lambda})^{2} \\
&= \frac{\mu}{2}\left(I_{C}-3\right) - \mu\left(J-1\right) + \frac{\lambda}{2}(J-1)^{2} + \left(\frac{\mu}{\lambda}\right)^{2}.
\end{align*}
Since constants disappear under differentiation this expression is functionally equivalent to 
\[
\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) - \mu\left(J-1\right) + \frac{\lambda}{2}(J-1)^{2}.
\]
Now we can see that $\Psi_{E}$ looks very similar to $\Psi_{Neo}$. The difference is that $log(J)$ is replaced with $(J-1)$ in $\Psi_{E}$. Keep in mind that $(J-1)$ is the first term in the taylor approximation of $\operatorname{log}(J)$ at $J=1$:
\begin{align*}
\sum_{n=0}^{\infty} &= \frac{f^{(n)}(1)}{n!} (J-1)^{n} \\
&= \boldsymbol{(J-1)} - \frac{1}{2} (J-1)^{2} + \frac{1}{3} (J-1)^{3} -\frac{1}{4} (J-1)^{4} + \text{...}
\end{align*}
Thus $\Psi_{E}$ is an approximation of $\Psi_{Neo}$.

@@

\subsection{Meta-Stability under Degeneracy}
The final energy is
\begin{equation}\label{eq:stable_energy}
\Psi_{new} = \frac{\mu}{2}\left(I_{C}-3\right) + \frac{\lambda}{2}(J-\alpha)^{2} - \frac{\mu}{2} \operatorname{log}\left(I_{C}+1\right).
\end{equation}
With that adjustment the rest stability term can be written as $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$.

@@

\section{Energy Analysis}
The goal of this chapter is to show that a complete eigenanalysis can be performed on Eq. \ref{eq:stable_energy}.

\subsection{First Piola-Kirchhoff Stress (PK1)}
In order to analyse the energy PK1 can be used for Eq. \ref{eq:stable_energy}:
\begin{align*}
P(\mathbf{F}) &= \frac{\partial \Psi_{D}}{\partial \mathbf{F}} \left[ \frac{\mu}{2}\left(I_{C}-3\right) + \frac{\lambda}{2}(J-\alpha)^{2} - \frac{\mu}{2}\left(I_{C}+1\right) \right] \\
&= \mu \mathbf{F} + \lambda (\operatorname{det}(\mathbf{F})-\alpha)  \frac{\partial}{\partial \mathbf{F}} \operatorname{det}(\mathbf{F}) - \frac{\partial}{\partial \mathbf{F}} \left[\operatorname{log}\left(\operatorname{tr}(\mathbf{F}^\intercal \mathbf{F})+1\right)\right] \\
&= \mu \mathbf{F} + \lambda (\operatorname{det}(\mathbf{F})-\alpha)  \frac{\partial}{\partial \mathbf{F}} \operatorname{det}(\mathbf{F}) - \mu \mathbf{F} \frac{1}{\operatorname{tr}(\mathbf{F}^\intercal \mathbf{F}) + 1} \\
&= \mu \left( 1 - \frac{1}{\operatorname{tr}(\mathbf{F}^\intercal \mathbf{F}) + 1}\right) \mathbf{F} + \lambda(J-\alpha)\frac{\partial J}{\partial \mathbf{F}}
\end{align*}

with $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$. For further use it can be more practical to write $\frac{\partial J}{\partial \mathbf{F}}$ as a result of cross products:
\begin{equation}\label{eq:cross_product}
\frac{\partial J}{\partial \mathbf{F}} = \left[ \,f_1 \times f_2\, \bigg| \,f_2 \times f_0\, \bigg| \,f_0 \times f_1\, \right].
\end{equation}

@@

\subsection{The Energy Hessian Terms}
Using the scalar notation for $\mathbf{F}$, the Hessian of the energy can be written as a fourth-order matrix-of-matrices:
\[
\frac{\partial^2 \psi}{\partial \mathbf{F}^2} = \frac{\partial P(\mathbf{F})}{\partial \mathbf{F}} = 
\left[\begin{array}{ccc}{\left[\frac{\partial P(\mathbf{F})}{\partial f_0}\right]} & {\left[\frac{\partial P(\mathbf{F})}{\partial f_3}\right]} & {\left[\frac{\partial P(\mathbf{F})}{\partial f_6}\right]} \\ {\left[\frac{\partial P(\mathbf{F})}{\partial f_1}\right]} & {\left[\frac{\partial P(\mathbf{F})}{\partial f_4}\right]} & {\left[\frac{\partial P(\mathbf{F})}{\partial f_7}\right]} \\ {\left[\frac{\partial P(\mathbf{F})}{\partial f_2}\right]} & {\left[\frac{\partial P(\mathbf{F})}{\partial f_5}\right]} & {\left[\frac{\partial P(\mathbf{F})}{\partial f_8}\right]} \end{array}\right]
\]

in which each entry is defined as
\[
\frac{\partial P(\mathbf{F})}{\partial f_i} = \frac{\partial}{\partial f_i} \left[ \mu \left( 1 - \frac{1}{\operatorname{tr}(\mathbf{F}^\intercal \mathbf{F}) + 1}\right) \mathbf{F} + \lambda(J-\alpha)\frac{\partial J}{\partial \mathbf{F}} \right]
\]
\[
\stackrel{\text{prod.rule}}{=} \underbrace{\frac{\partial \mathbf{F}}{\partial f_i} \mu \left( 1 - \frac{1}{\operatorname{tr}(\mathbf{F}^\intercal \mathbf{F}) + 1}\right)}_{\mathrm{T}_{i}}  + \underbrace{\mathbf{F} \mu \frac{2}{\left(\operatorname{tr}(\mathbf{F^\intercal}\mathbf{F}) + 1\right)^2} f_i}_{_{\mathrm{M}_{i}}}
\]
\[
r+ \underbrace{\lambda \frac{\partial J}{\partial f_i} \frac{\partial J}{\partial \mathbf{F}}}_{_{\mathrm{G}_{i}}}+ \underbrace{\lambda (J- \alpha) \frac{\partial^2 J}{\partial \mathbf{F}\partial f_i}}_{_{\mathrm{H}_{i}}} \in \mathbb{R}^{3}.
\]
We can split up this final equation into these four term: $\mathrm{T}_i$ (Tikohonov), $\mathrm{M}_i$ (Mu), $\mathrm{G}_i$ (Volume Gradient), $\mathrm{H}_i$ (Volume Hessian). I will examine them separately in the next section.

\subsection{The Tikhonov, Mu, and Gradient Terms}
\subsubsection{Tikhonov}
The Tikhonov term is a fourth-order matrix-of-matrices
\[
\mathbb{T} = \frac{\partial \mathbf{F}}{\partial f_i} = \left[\begin{array}{ccc}{\begin{bmatrix} 1 & 0 & 0 \\ 0 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 1 & 0 \\ 0 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 1 \\ 0 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} \\ {\begin{bmatrix} 0 & 0 & 0 \\ 1 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 1 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 1 \\ 0 & 0 & 0 \end{bmatrix}} \\ {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 0 \\ 1 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 0 \\ 0 & 1 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 0 \\ 0 & 0 & 1 \end{bmatrix}} \end{array}\right].
\]
If we vectorize $\mathbb{T}$, we get the identity matrix $\mathbf{I} \in \mathbb{R}^{9x9}$ which is of full rank, positive definite and independent of the values in \textbf{F}. 
\[
\operatorname{vec}(\mathbb{T}) =  \mathbf{\check{T}} = \mathbf{I} = \in \mathbb{R}^{9x9}.
\]
It serves as a regularizer for the rest of the energy.

\subsubsection{Mu}
The Mu term has the same structure with different entries
\[
\mathbb{M} = \mathbf{F} f_i = \left[\begin{array}{ccc}{\begin{bmatrix} f_0^2 & f_0f_3 & f_0f_6 \\ f_0f_1 & f_0f_4 & f_0f_7 \\ f_0f_2 & f_0f_5 & f_0f_8 \end{bmatrix}} & {\begin{bmatrix} f_3f_0 & f_3^2 & f_3f_6 \\ f_3f_1 & f_3f_4 & f_3f_7 \\ f_3f_2 & f_3f_5 & f_3f_8 \end{bmatrix}} & {\begin{bmatrix} f_6f_0 & f_6f_3 & f_6f_6 \\ f_6f_1 & f_6f_4 & f_6f_7 \\ f_6f_2 & f_6f_5 & f_6f_8 \end{bmatrix}} \\ {\begin{bmatrix} f_1f_0 & f_1f_3 & f_1f_6 \\ f_1^2 & f_1f_4 & f_1f_7 \\ f_1f_2 & f_1f_5 & f_1f_8 \end{bmatrix}} & {\begin{bmatrix} f_4f_0 & f_4f_3 & f_4f_6 \\ f_4f_1 & f_4^2 & f_4f_7 \\ f_4f_2 & f_4f_5 & f_4f_8 \end{bmatrix}} & {\begin{bmatrix} f_7f_0 & f_7f_3 & f_7f_6 \\ f_7f_1 & f_7f_4 & f_7^2 \\ f_7f_2 & f_7f_5 & f_7f_8 \end{bmatrix}} \\ {\begin{bmatrix} f_2f_0 & f_2f_3 & f_2f_6 \\ f_2f_1 & f_2f_4 & f_2f_7 \\ f_2^2 & f_2f_5 & f_2f_8 \end{bmatrix}} & {\begin{bmatrix} f_5f_0 & f_5f_3 & f_5f_6 \\ f_5f_1 & f_5f_4 & f_5f_7 \\ f_5f_2 & f_5^2 & f_5f_8 \end{bmatrix}} & {\begin{bmatrix} f_8f_0 & f_8f_3 & f_8f_6 \\ f_8f_1 & f_8f_4 & f_8f_7 \\ f_8f_2 & f_8f_5 & f_8^2 \end{bmatrix}} \end{array}\right].
\]
When vectorizing $\mathbb{M}$, the resulting matrix $\mathbf{\check{M}}$ has the squared values of $f_i$ placed on the diagonal
\[
\operatorname{vec}(\mathbb{M})= \mathbf{\check{M}} = \begin{bmatrix} f_0^2 & f_1f_0 & f_2f_0 & f_3f_0 & f_4f_0 & f_5f_0 & f_6f_0 & f_7f_0 & f_8f_0 \\ f_0f_1 & f_1^2 & f_2f_1 & f_3f_1 & f_4f_1 & f_5f_1 & f_6f_1 & f_7f_1 & f_8f_1 \\ f_0f_2 & f_1f_2 & f_2^2 & f_3f_2 & f_4f_2 & f_5f_2 & f_6f_2 & f_7f_2 & f_8f_2 \\ f_0f_3 & f_1f_3 & f_2f_3 & f_3^2 & f_4f_3 & f_5f_3 & f_6f_3 & f_7f_3 & f_8f_3 \\ f_0f_4 & f_1f_4 & f_2f_4 & f_3f_4 & f_4^2 & f_5f_4 & f_6f_4 & f_7f_4 & f_8f_4 \\ f_0f_5 & f_1f_5 & f_2f_5 & f_3f_5 & f_4f_5 & f_5^2 & f_6f_5 & f_7f_5 & f_8f_5 \\ f_0f_6 & f_1f_6 & f_2f_6 & f_3f_6 & f_4f_6 & f_5f_6 & f_6^2 & f_7f_6 & f_8f_6 \\ f_0f_7 & f_1f_7 & f_2f_7 & f_3f_7 & f_4f_7 & f_5f_7 & f_6f_7 & f_7^2 & f_8f_7 \\ f_0f_8 & f_1f_8 & f_2f_8 & f_3f_8 & f_4f_8 & f_5f_8 & f_6f_8 & f_7f_8 & f_8^2 \end{bmatrix}.
\]
This structure makes it possible to write $\mathbf{\check{M}}$ as an outer product of $\operatorname{vec}(\mathbf{F})$
\[
\mathbf{\check{M}}= \operatorname{vec}(\mathbf{F})\operatorname{vec}(\mathbf{F})^\intercal = \mathbf{\check{f}} \mathbf{\check{f}}^\intercal.
\]
This matrix has rank one and has a single non-zero eigenvalue. In order to examine the eigenvalues, we can calculate
\[
\| \mathbf{\check{f}} \|^{2}_{2} = \sum_{n=0}^8 | f_n |^2 = \| \mathbf{F} \|^{2}_{F} = \sum_{n=0}^3 \sigma^2_i = \left( \sigma_0^2 + \sigma_1^2 + \sigma_2^2 \right)
\]
in which $\|\cdot\|_F$ stands for the Frobenius norm and $\sigma_i$ for the singular values from $\mathbf{\Sigma}$ in the SVD of $\mathbf{F}$ stated in Eq. \ref{eq:svd_simga}. The eigenvector is $\mathbf{\check{f}} / \| \mathbf{\check{f}} \|$. The eigenvalue is always non-negative and large if $\mathbf{F}$ contains a large strech.
